Production experiment

### 2021-01-05 osf/comps/data/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

This directory contains 3 subdirectories: `Materials/`, `Raw data/`, and `TextGrids/`.
See the `README.md` files of each individual directory for more information about the contents.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

>>>>

This directory contains 2 subdirectories: `exp-materials/` and `data/`.

Files and results of the norming study are in `exp-materials/`
The `data` directory hosts the `.wav` and `.TextGrid` files from the production experiment.
See the `README.md` files of each individual directory for more information about the contents.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

### 2021-01-05 osf/comps/data/exp-materials/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

---
title: "Materials"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the images, trial lists, and the results from the norming study.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Materials") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Experiment materials"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the files used for the norming study and for the production experiment:

- The `norming/` directory hosts the images of the objects with modified color used in the norming study and the results (ratings) of the study.
- The `experiment/` directory contains the randomization lists for each participant in the production study.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "exp-materials") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

---
title: "Norming results"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the results from the norming study.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Materials/Norming results") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Production experiment"
output:
  github_document:
    html_preview: false
---

@@

This directory contains one `.csv` file per participant from the production experiment with information about the trials (one row per trial).

The files include the following columns:

- `condition`: The condition of the trial (`NF` = noun focus, `AF` = adjective focus, `ANF` = adjective/noun focus).
- `target_name`: Name of the target object.
- `target_colour`: Color of the target object.
- `competitor_name`: Name of the competitor object.
- `competitor_colour`: Color of the competitor object.
- `distractor1_name`: Name of the distractor 1.
- `distractor1_colour`: Color of the distractor 1.
- `distractor2_name`: Name of the distractor 2.
- `distractor2_colour`: Color of the distractor 2.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=FALSE}
osf_ls_files(data_comp, "exp-materials/experiment") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```
